Explaining Amsterdam House Prices with Greenness

### 2023-04-11 README.Rmd
readme

# Stucture of the directory
The way the data analysis was performed is described in the figure below. Below headers provide some insight into the steps that were taken during each phase.

![Overview of methods](Paper/figures/Methods.jpg)

@@

The used data regarding the Public Amenities can be found in the [/data/Amsterdam/ folder](https://github.com/JitseRuurd/Amsterdam_Urban_Green/tree/main/data/Amsterdam) and partly in the [1.c Data Enrichment script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1c.%20Data%20enrichment.R).

The House price data was extracted with the help of the Funda-Scraper package. This code was however modified to be able to extract a more precise adress line, which could be used for geocoding the adress to spatial data.

The [Funda scraper notebook](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/Scraper/Scraper.ipynb) provides code to copy the code of the enhanced funda scraper in the site-packages or dist-packages directory of python:

@@

![Overview of results](Paper/Figures/Economic_Value_Urban_Green_clip.png)

>>>>

# Stucture of the directory
The way the data analysis was performed is described in the figure below. The text after the figure provides some insight into the steps that were taken during each phase.

![Overview of methods](Paper/figures/Methods.png)

@@

The used data regarding the Public Amenities can be found in the [/data/Amsterdam/ folder](https://github.com/JitseRuurd/Amsterdam_Urban_Green/tree/main/data/Amsterdam) and partly in the [1.c Data Enrichment script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1c.%20Data%20enrichment.R). The data sources consisted of the Municipality of Amsterdam, ArGIS and OSM.

The House price data was extracted with the help of the Funda-Scraper package. This code was however modified to be able to extract a more precise address line, which could be used for geocoding the address to spatial data.

The [Funda scraper notebook](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/Scraper/Scraper.ipynb) provides code to copy the code of the enhanced Funda scraper in the site-packages or dist-packages directory of python:

@@

![Overview of results](Paper/figures/Economic_Value_Urban_Green_clip.png)
